---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# castarter.readability

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `castarter.readability` is to extract text and metadata from web pages through `readability.js`. As the name suggests, this is a companion package to [`castarter`](https://github.com/giocomai/castarter) - Content Analysis Starter Toolkit for the R programming language.

This package sticks together various elements of pre-existing libraries (see below for references and licenses details) for easier embedding in workflows. The R implementation is based on [this tutorial](https://nanx.me/blog/post/r-readability-parser/) / [see repo](https://github.com/nanxstats/r-readability-parser/), which is partly based on this [V8 vignette](https://cran.r-project.org/web/packages/V8/vignettes/npm.html). All of the credits go to respective authors. 

## Installation

You can install the development version of `castarter.readability` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("giocomai/castarter.readability")
```

## Embedded libraries

This package embeds dependencies. Newer versions may be available by the time you see this. In order to pack these dependencies, follow the above-mentioned tutorials. In brief, these are the key steps. 

- make sure you have `browserify` installed (`npm install -g browserify`)
- pack `readability.js`, `jsdom.js`, and `dompurify.js`

```
npm install @mozilla/readability
echo "window.Readability = require('@mozilla/readability');" > in.js
browserify in.js -o readability.js

npm install jsdom@20.0.0
echo "window.jsdom = require('jsdom');" > in.js
browserify in.js -o jsdom.js

npm install dompurify
echo "window.dompurify = require('dompurify');" > in.js
browserify in.js -o dompurify.js
```

- in order to prevent encoding issues, include [`encoding.min.js`](https://cdn.jsdelivr.net/npm/text-encoding@0.7.0/lib/encoding.min.js)


Following the above-mentioned [`V8` vignette](https://cran.r-project.org/web/packages/V8/vignettes/npm.html)

## Example



```{r}
library("castarter.readability")

url <- "https://giorgiocomai.eu/post/2020-06-abkhazia-gorecki/"


html_source <- readLines(con = url, warn = FALSE) |>
  paste0(collapse = "\n")

cas_extract_readability_check(html = html_source)
```

```{r}
extracted_readability_list <- cas_extract_readability(html = html_source, url = url)

str(extracted_readability_list)
```


